<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{solr vignette}
-->

solr vignette
======

**A general purpose R interface to [Solr](http://lucene.apache.org/solr/)**

This package only deals with extracting data from a Solr endpoint, not writing data (pull request or holla if you're interested in writing solr data).

### Solr info

+ [Solr home page](http://lucene.apache.org/solr/)
+ [Highlighting help](http://wiki.apache.org/solr/HighlightingParameters)
+ [Faceting help](http://wiki.apache.org/solr/SimpleFacetParameters)
+ [Installing Solr on Mac using homebrew](http://ramlev.dk/blog/2012/06/02/install-apache-solr-on-your-mac/)
+ [Install and Setup SOLR in OSX, including running Solr](http://risnandar.wordpress.com/2013/09/08/how-to-install-and-setup-apache-lucene-solr-in-osx/)

### Quick start

**Install**

Install dependencies

```{r, eval=FALSE}
install.packages(c("rjson","plyr","httr","XML","assertthat"))
```

Install solr

```{r, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("ropensci/solr")
```

```{r}
library(solr)
```

**Define stuff** Your base url and a key (if needed). This example should work. You do need to pass a key to the Public Library of Science search API, but it apparently doesn't need to be a real one.

```{r}
url <- 'http://api.plos.org/search'
key <- 'key'
```

**Search**

```{r}
solr_search(q='*:*', rows=2, fl='id', base=url, key=key)
```

**Facet**

```{r}
solr_facet(q='*:*', facet.field='journal', facet.query=c('cell','bird'), base=url, key=key)
```

**Highlight**

```{r}
solr_highlight(q='alcohol', hl.fl = 'abstract', rows=2, base = url, key=key)
```

**Stats**

```{r}
out <- solr_stats(q='ecology', stats.field=c('counter_total_all','alm_twitterCount'), stats.facet=c('journal','volume'), base=url, key=key)
```

```{r}
out$data
```

```{r}
out$facet
```

**More like this**

`solr_mlt` is a function to return similar documents to the one 

```{r}
out <- solr_mlt(q='title:"ecology" AND body:"cell"', mlt.fl='title', mlt.mindf=1, mlt.mintf=1, fl='counter_total_all', rows=5, base=url, key=key)
out$docs
```

```{r}
out$mlt
```

**Parsing**

`solr_parse` is a general purpose parser function with extension methods `solr_parse.sr_search`, `solr_parse.sr_facet`, and `solr_parse.sr_high`, for parsing `solr_search`, `solr_facet`, and `solr_highlight` function output, respectively. `solr_parse` is used internally within those three functions (`solr_search`, `solr_facet`, `solr_highlight`) to do parsing. You can optionally get back raw `json` or `xml` from `solr_search`, `solr_facet`, and `solr_highlight` setting parameter `raw=TRUE`, and then parsing after the fact with `solr_parse`. All you need to know is `solr_parse` can parse 

For example:

```{r}
(out <- solr_highlight(q='alcohol', hl.fl = 'abstract', rows=2, base = url, key=key, raw=TRUE))
```

Then parse

```{r}
solr_parse(out, 'df')
```

**Using specific data sources**

*USGS BISON service*

The occurrences service

```{r}
url2 <- "http://bison.usgs.ornl.gov/solrstaging/occurrences/select"
solr_search(q='*:*', fl=c('decimalLatitude','decimalLongitude','scientificName'), base=url2)
```

*PLOS Search API*

Most of the examples above use the PLOS search API... :)


[Please report any issues or bugs](https://github.com/ropensci/solr/issues).
