<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Solr search}
%\VignetteEncoding{UTF-8}
-->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

Solr search
===========

**A general purpose R interface to [Apache Solr](http://lucene.apache.org/solr/)**

This package only deals with extracting data from a Solr endpoint, not writing data (pull request or holla if you're interested in writing solr data).

## Solr info

+ [Solr home page](http://lucene.apache.org/solr/)
+ [Highlighting help](http://wiki.apache.org/solr/HighlightingParameters)
+ [Faceting help](http://wiki.apache.org/solr/SimpleFacetParameters)
+ [Installing Solr on Mac using homebrew](http://ramlev.dk/blog/2012/06/02/install-apache-solr-on-your-mac/)
+ [Install and Setup SOLR in OSX, including running Solr](http://risnandar.wordpress.com/2013/09/08/how-to-install-and-setup-apache-lucene-solr-in-osx/)

## Installation

Stable version from CRAN

```{r eval=FALSE}
install.packages("solr")
```

Or the development version from GitHub

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("ropensci/solr")
```

Load

```{r}
library("solr")
```

## Define url for Solr instance

This url can be a remote Solr instance or on your local machine.

```{r}
url <- 'http://api.plos.org/search'
```

## Rundown

`solr_search()` only returns the `docs` element of a Solr response body. If `docs` is 
all you need, then this function will do the job. If you need facet data only, or mlt 
data only, see the appropriate functions for each of those below. Another function, 
`solr_all()` has a similar interface in terms of parameter as `solr_search()`, but 
returns all parts of the response body, including, facets, mlt, groups, stats, etc.
as long as you request those. 

## Search docs

`solr_search()` returns only docs. A basic search:

```{r}
solr_search(q = '*:*', rows = 2, fl = 'id', base = url)
```

__Search in specific fields with `:`__ 

Search for word ecology in title and cell in the body

```{r}
solr_search(q = 'title:"ecology" AND body:"cell"', fl = 'title', rows = 5, base = url)
```

__Wildcards__ 

Search for word that starts with "cell" in the title field

```{r}
solr_search(q = 'title:"cell*"', fl = 'title', rows = 5, base = url)
```

__Proximity search__

Search for words "sports" and "alcohol" within four words of each other

```{r}
solr_search(q = 'everything:"stem cell"~7', fl = 'title', rows = 3, base = url)
```

__Range searches__

Search for articles with Twitter count between 5 and 10

```{r}
solr_search(q = '*:*', fl = c('alm_twitterCount', 'id'), fq = 'alm_twitterCount:[5 TO 50]', 
rows = 10, base = url)
```

__Boosts__

Assign higher boost to title matches than to body matches (compare the two calls)

```{r}
solr_search(q = 'title:"cell" abstract:"science"', fl = 'title', rows = 3, base = url)
```

```{r}
solr_search(q = 'title:"cell"^1.5 AND abstract:"science"', fl = 'title', rows = 3, base = url)
```

## Search all

`solr_all()` differs from `solr_search()` in that it allows specifying facets, mlt, groups, 
stats, etc, and returns all of those. It defaults to `parsetype = "list"` and `wt="json"`, 
whereas `solr_search()` defaults to `parsetype = "df"` and `wt="csv"`. `solr_all()` returns 
by default a list, whereas `solr_search()` by default returns a data.frame.

A basic search, just docs output

```{r}
solr_all(q = '*:*', rows = 2, fl = 'id', base = url)
```

Get docs, mlt, and stats output

```{r}
solr_all(q = 'ecology', rows = 2, fl = 'id', base = url, mlt = 'true', mlt.count = 2, mlt.fl = 'abstract', stats = 'true', stats.field = 'counter_total_all')
```


## Facet

```{r}
solr_facet(q = '*:*', facet.field = 'journal', facet.query = c('cell', 'bird'), base = url)
```

## Highlight

```{r}
solr_highlight(q = 'alcohol', hl.fl = 'abstract', rows = 2, base = url)
```

## Stats

```{r}
out <- solr_stats(q = 'ecology', stats.field = c('counter_total_all', 'alm_twitterCount'), stats.facet = c('journal', 'volume'), base = url)
```

```{r}
out$data
```

```{r}
out$facet
```

## More like this

`solr_mlt` is a function to return similar documents to the one

```{r}
out <- solr_mlt(q = 'title:"ecology" AND body:"cell"', mlt.fl = 'title', mlt.mindf = 1, mlt.mintf = 1, fl = 'counter_total_all', rows = 5, base = url)
out$docs
```

```{r}
out$mlt
```

## Groups

`solr_groups()` is a function to return similar documents to the one

```{r}
solr_group(q = 'ecology', group.field = 'journal', group.limit = 1, fl = c('id', 'alm_twitterCount'), base = url)
```

## Parsing

`solr_parse()` is a general purpose parser function with extension methods for parsing outputs from functions in `solr`. `solr_parse()` is used internally within functions to do parsing after retrieving data from the server. You can optionally get back raw `json`, `xml`, or `csv` with the `raw=TRUE`, and then parse afterwards with `solr_parse()`.

For example:

```{r}
(out <- solr_highlight(q = 'alcohol', hl.fl = 'abstract', rows = 2, base = url, raw = TRUE))
```

Then parse

```{r}
solr_parse(out, 'df')
```

[Please report any issues or bugs](https://github.com/ropensci/solr/issues).
